### 2019-01-21 writing/thesis/chapters/results.tex
Small tweaks.

\sidetitle{Lid-Driven Cavity}
\begin{figure}[htb]
  \centering
  \begin{subfigure}[t]{0.5\textwidth}
    \centering
    \includegraphics[]{thesis_lid_driven_cavity_stream}
    \caption{\label{fig:lid-driven-cavity-streamlines}%
      Streamlines of the cavity flow.}
  \end{subfigure}~%
  \begin{subfigure}[t]{0.5\textwidth}
    \centering
    \includegraphics{thesis_lid_driven_cavity}
    \caption{\label{fig:lid-driven-cavity-result}%
      Plot of velocity slices. Lines are our soulution, scatter plot shows reference solution~\cite{ghia1982high}.
      For each slice, the other variable is hold constant at the center of the domain (0).}
  \end{subfigure}

@@

\section{Accurate Clouds}\label{sec:results-cloud}
We discussed the capabilities of our scheme regarding standard \textsc{cfd} testing scenario.
In this section, we consider our bubble scenarios.
\sidetitle{Cosine Bubble}
\begin{figure}[htb]
  \centering
  \begin{subfigure}[t]{0.5\textwidth}
    \centering
    \includegraphics[scale=1.0]{thesis_cosine_bubble_contour_t700}
    \caption{\label{fig:cosine-bubble-contour-ours}%
      Our result}
  \end{subfigure}~%
  \begin{subfigure}[t]{0.5\textwidth}
    \centering
    \includegraphics{giraldo_results_cosine_bubble}
    \caption{\label{fig:cosine-bubble-contour-giraldo}%
      Figure taken from~\cite{giraldo2008study}, resolution of \SI{20}{\m}, $N = 10$, \dg{}, modified Navier-Stokes} %poly order
  \end{subfigure}
  \caption{\label{fig:cosine-bubble-contour}%
    Contours for the cosine bubble results.
    Contours are $-0.05, -0.025, \ldots 0.525$, excluding zero.
  }
\end{figure}
We ran our first scenario, the cosine bubble~\pcref{eq:cosine-bubble}, with an \aderdg{}-scheme of order 4 and the adaptive mesh criterion \cref{eq:refinement-criterion} with thresholds of $T_\text{refine} = 2.5$ and $T_\text{delete} = -0.5$ and the total variation of the potential temperature $\potT$ as indicator variable.
Our coarsest level had $3^3$ cells, our finest level had $3^4$ cells.
We thus had a resolution of ca.\ \SI{37.037}{\m} up to \SI{12.3457}{\m}.

@@

\begin{figure}[htb]
  \centering
  \begin{subfigure}[t]{0.5\textwidth}
    \centering
    \includegraphics{thesis_cosine_bubble_pertubation}
    \caption{\label{fig:cosine-bubble-potT-ours}%
      Our result}
  \end{subfigure}~%
  \begin{subfigure}[t]{0.5\textwidth}
    \centering
    \includegraphics{giraldo_results_cosine_bubble_pertubation}
    \caption{\label{fig:cosine-bubble-potT-giraldo}%
      Figure taken from~\cite{giraldo2008study}, resolution of \SI{20}{\m}, $N = 10$, \dg{}3 uses modified Navier-Stokes} %poly order
  \end{subfigure}
  \caption{\label{fig:cosine-bubble-potT}%
    Height $z$ vs.\ pertubation of potential temperature for the cosine bubble scenario at $t=\SI{700}{\s}$ and $x = \SI{500}{\m}$.
  }
\end{figure}

@@

% \begin{figure}[p]
%   \vspace*{-4.5cm}
%   \thisfloatpagestyle{empty}
%   \centering
%   \begin{subfigure}{1\textwidth}
%     \centering
%     \includegraphics{thesis_two_bubbles_contour_collage.pdf}
%   \end{subfigure}
%   \vspace*{1cm}
%   \begin{subfigure}[t]{1\textwidth}
%     \centering
%     \includegraphics[trim=0.0cm 0.0cm 0.0cm 0.0cm, clip, scale=1.2]{giraldo_results_two_bubbles}
%   \end{subfigure}
%   \caption{\label{fig:two-bubbles-contour}%
%     Results for two bubble scenario.
%     On the top is our, the bottom plots are taken from~\cite{muller2010adaptive}.
%   Contour values for potential temperature pertubation are $-0.05, 0.05, 0.1, \ldots 0.45$.
% }
% \end{figure}
\begin{figure}[p]
  \thisfloatpagestyle{empty}
  \centering
  \begin{subfigure}[t]{0.5\textwidth}
    \centering
  \includegraphics[trim={0cm 0cm 6cm 0cm},clip]{thesis_two_bubbles_contour_collage_comparison} 
  \caption{Our \amr{} solution.}
  \end{subfigure}~%
  \begin{subfigure}[t]{0.5\textwidth}
    \centering
  % Without z axis on right \includegraphics[trim={8.16cm 0cm 0cm 0cm},clip]{thesis_two_bubbles_contour_collage_comparison} 
  \includegraphics[trim={7.4cm 0cm 0cm 0cm},clip]{thesis_two_bubbles_contour_collage_comparison} 
  \caption{Reference solution from~\cite{muller2010adaptive}.}
  \end{subfigure}
  \caption{\label{fig:two-bubbles-contour}%
     Contours of the potential temperature for two bubble scenario.
     On the left is our solution, the right plots are taken from~\cite{muller2010adaptive}.
     We modified the arrangement of the reference plots and the placement of its axes. 
   Contour values for potential temperature pertubation are $-0.05, 0.05, 0.1, \ldots 0.45$.
  }
\end{figure}

@@

% \begin{figure}[htb]
%   \centering
%   \includegraphics{thesis_two_bubbles_contour_t600_noamr} 
%   \caption{\label{fig:two-bubbles-noamr-contour}%
%     Two bubbles run with fully refined mesh}
% \end{figure}
For both settings, we used an \aderdg{}-method of order $4$ and thus have a minimal effective resolution of ca.\ $\SI{3.09}{\m}$.
%The final result for the run with the fully refined mesh (\cref{fig:two-bubbles-noamr-contour}) looks identical to the \amr{} results (\cref{fig:two-bubbles-contour}) shown in the previous section.
Note that the \amr{} criterion manages to track the bubble correctly~(\cref{fig:two-bubbles-amr-grid}) and introduces only small errors~(\cref{fig:two-bubbles-amr-error}) compared to the solution with the fully refined mesh\todo{Increase font size a bit more}.

>>>>

\sidetitle{Lid-Driven Cavity}
\begin{figure}[htb]
  \centering
  \begin{subfigure}[t]{0.5\textwidth}
    \centering
    \includegraphics[trim={0.05cm 0.05cm 0.55cm 1.0cm},clip]{thesis_lid_driven_cavity_stream}
    \caption{\label{fig:lid-driven-cavity-streamlines}%
      Streamlines of the cavity flow.}
  \end{subfigure}~%
  \begin{subfigure}[t]{0.5\textwidth}
    \centering
    \includegraphics{thesis_lid_driven_cavity}
    \caption{\label{fig:lid-driven-cavity-result}%
      Plot of velocity slices. Lines are our soulution, scatter plot shows reference solution~\cite{ghia1982high}.
      For each slice, the other variable is hold constant at a value of zero.}
  \end{subfigure}

@@

\section{Accurate Clouds}\label{sec:results-cloud}
We discussed the capabilities of our scheme regarding standard \textsc{cfd} testing scenario.
In this section, we consider our bubble scenarios.
\sidetitle{Cosine Bubble}
\begin{figure}[htb]
  \centering
  \begin{subfigure}[t]{0.5\textwidth}
    \centering
    \includegraphics[trim={0.00cm 0.00cm 6.35cm 0.0cm},clip]{thesis_cosine_bubble_contour_comparison}
    \caption{\label{fig:cosine-bubble-contour-ours}%
      Our result}
  \end{subfigure}~%
  \begin{subfigure}[t]{0.5\textwidth}
    \centering
    \includegraphics[trim={6.8cm 0.00cm 0cm 0.0cm},clip]{thesis_cosine_bubble_contour_comparison}
    \caption{\label{fig:cosine-bubble-contour-giraldo}%
      Figure taken from~\cite{giraldo2008study}, resolution of \SI{20}{\m}, $N = 10$, \dg{}, modified Navier-Stokes} %poly order
  \end{subfigure}
  \caption{\label{fig:cosine-bubble-contour}%
    Contours for the cosine bubble results.
    Contours are $-0.05, -0.025, \ldots 0.525$, excluding zero.
  }
\end{figure}
We ran our first scenario, the cosine bubble~\pcref{eq:cosine-bubble}, with an \aderdg{}-scheme of order 4 and the adaptive mesh criterion \cref{eq:refinement-criterion} with thresholds of $T_\text{refine} = 2.5$ and $T_\text{delete} = -0.5$ and the total variation of the potential temperature $\potT$ as indicator variable.
Our coarsest level had $3^3$ cells, our finest level had $3^4$ cells.
We thus had a resolution of ca.\ \SI{37.037}{\m} up to \SI{12.3457}{\m}.

@@

\begin{figure}[htb]
  \centering
  \begin{subfigure}[t]{0.45\textwidth}
    \centering
    \includegraphics[trim={0.00cm 0.00cm 8.4cm 0.0cm},clip]{thesis_cosine_bubble_pertubation_comparison}
    \caption{\label{fig:cosine-bubble-potT-ours}%
      Our result}
  \end{subfigure}~%
  \begin{subfigure}[t]{0.55\textwidth}
    \centering
    \includegraphics[trim={7.00cm 0.00cm 0.0cm 0.0cm},clip]{thesis_cosine_bubble_pertubation_comparison}
    \caption{\label{fig:cosine-bubble-potT-giraldo}%
      Figure taken from~\cite{giraldo2008study}, resolution of \SI{20}{\m}, $N = 10$, \dg{}3 uses modified Navier-Stokes} %poly order
  \end{subfigure}
  \caption{\label{fig:cosine-bubble-potT}%
    Height $z$ vs.\ pertubation of potential temperature for the cosine bubble scenario at $t=\SI{700}{\s}$ and $x = \SI{500}{\m}$.
  }
\end{figure}

@@

\begin{figure}[p]
  \thisfloatpagestyle{empty}
  \vspace*{-1cm}
  \centering
  \begin{subfigure}[t]{0.5\textwidth}
    \centering
  \includegraphics[trim={0cm 0cm 5.6cm 0cm},clip]{thesis_two_bubbles_contour_collage_comparison} 
  \caption{Our \amr{} solution.}
  \end{subfigure}~%
  \begin{subfigure}[t]{0.5\textwidth}
    \centering
  % Without z axis on right \includegraphics[trim={8.16cm 0cm 0cm 0cm},clip]{thesis_two_bubbles_contour_collage_comparison} 
  \includegraphics[trim={6.2cm 0cm 0cm 0cm},clip]{thesis_two_bubbles_contour_collage_comparison} 
  \caption{Reference solution from~\cite{muller2010adaptive}.}
  \end{subfigure}
  \caption{\label{fig:two-bubbles-contour}%
     Contours of the potential temperature for two bubble scenario.
     On the left is our solution, the right plots are taken from~\cite{muller2010adaptive}.
     We rescaled the reference plots and changed their arrangement and axes placement.
   Contour values for potential temperature pertubation are $-0.05, 0.05, 0.1, \ldots 0.45$.
  }
\end{figure}

@@

% \begin{figure}[htb]
%   \centering
%   \includegraphics{thesis_two_bubbles_contour_t600_noamr} 
%   \caption{\label{fig:two-bubbles-noamr-contour}%
%     Two bubbles run with fully refined mesh}
% \end{figure}
For both settings, we used an \aderdg{}-method of order $4$ and thus have a minimal effective resolution of ca.\ $\SI{3.09}{\m}$.
%The final result for the run with the fully refined mesh (\cref{fig:two-bubbles-noamr-contour}) looks identical to the \amr{} results (\cref{fig:two-bubbles-contour}) shown in the previous section.
Note that the \amr{} criterion manages to track the bubble correctly~(\cref{fig:two-bubbles-amr-grid}) and introduces only small errors~(\cref{fig:two-bubbles-amr-error}) compared to the solution with the fully refined mesh.
